---
title: "EEZ map for every OHI region"
author: "Camila Vargas"
date: "8/23/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document creates one global map for each region highlighting their EEZ and on "zoon-in" map per region indication their eez. This was done as part of the OHI global fellowship as an independent project.

## Setup

```{r}

library(doParallel)
library(rgdal)
library(raster)
library(sf)
library(tidyverse)
library(cowplot)
library(ggmap)
library(lwgeom)

source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2018/master/src/R/spatial_common.R')

#setwd("~/github/global-viz/region_maps")


```


### Region "zoom-in" map
For this maps we are going to use the low resolution shapefile find in [this folder](https://github.com/OHI-Science/ohiprep/tree/master/globalprep/spatial/downres) to extract the eex per country and adding a base map using ggmaps.

```{r}
## Read the shape fill for all regions and filter for eez (our area of interest for these maps)

all_rgns <- sf::st_read('../../ohiprep/globalprep/spatial/downres', layer="rgn_all_gcs_med_res") %>%
  dplyr::filter(rgn_typ == "eez") %>% 
  dplyr::select(rgn_id, rgn_key, geometry) %>% 
  dplyr::arrange(rgn_id)


##validate the map so it can be ploted

all_rgns <- st_make_valid(all_rgns)
plot(all_rgns[1])



## Forloop to creat a map for each region.




```




### Test with on region

Before running the loop (and building the loop in this case Itested the method in one region, Chile)

```{r}
##Steps to creat each region map

## 1. Filter region of interest from all_rgn 
rgn_eez <- all_rgns %>%
  dplyr::filter(rgn_id== 224) ## For loop rgn_id == i?


## 2. Extract bounding box

rgn_bbox <- as.matrix(st_bbox(rgn_eez))
  

## 3. Create the base map with the corresponding bbox
rgn_loc <- rgn_bbox[1:4]
rgn_bmap <- get_map(location = rgn_bbox, zoom = 3, source = "google", maptype = "terrain", crop = FALSE)

plot(rgn_bmap)

## 4. Plot the eex and the base map. It is importatnt to do the CRS trasformation right before ploting both maps together in order to work.
st_crs(rgn_eez) <- 4326
rgn_tans <- st_transform(rgn_eez, crs = 3857)[1]
plot(st_geometry(rgn_tans), col = rgb(red = 1, green = 0, blue = 0, alpha = 0.2),border=NA, bgMap = rgn_bmap) #st_geometry removes the column name (rgn_id)


```


## Ceating inset maps for each region
The inset map is a map of the world highlighting each region eez.

```{r}

## Wrangle region object imported from spatiol_common.R
regions <- as(regions, "Spatial")
land <- regions[regions$rgn_type %in% c("land", "land-disputed", "land-noeez"), ]

# function to plot general regions
plot_rgn <- function(rgn){ #rgn="New Zealand"
  rgn_area <- regions[regions$rgn_name == rgn, ]  
  png(filename =str_to_lower(sprintf("figures/inset_maps/%s.png",str_replace(rgn, pattern = " ","_"))), res=500, width=7, height=7, units="in")
  plot(regions, col='#e3e7ea', border=NA)
  plot(land, col='gray85', border='grey80', add=TRUE, lwd=0.5)
  plot(rgn_area, col="red", border="red", add=TRUE)
  dev.off()
}

## Test the function for one region
plot_rgn("Chile")


##List with region names to loop over and create one inset map per region
region_list <- read_csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/spatial/regions_list.csv") 

##Loop through and save one map per region as a png
for (region in region_list$rgn_name[1:5]) {
 
  print(region)
  
  plot_rgn(rgn = region)  
}
```


## Combine both inset and zoom in region

```{r}

```


## Diferent approach using ggmap adn ggplot

```{r}

all_rgns <- regions %>% 
  dplyr::filter(rgn_type == "eez") %>% 
  dplyr::select(rgn_id, rgn_key, geometry) %>% 
  dplyr::arrange(rgn_id)



sf::st_crs(all_rgns) <- "+proj=longlat"
# now that you have the correct epsg set, reproject to 4326
all_rgns_repr = st_transform(all_rgns, 4326)


## trying different let long projections
# http://www.spatialreference.org/ref/esri/102718/proj4/
#+proj=lcc +lat_1=40.66666666666666 +lat_2=41.03333333333333 +lat_0=40.16666666666666 +lon_0=-74 +x_0=300000 +y_0=0 +ellps=GRS80 +datum=NAD83 +to_meter=0.3048006096012192 +no_defs 

"+proj=merc +lon_0=0 +k=1 +x_0=0 +y_0=0 +a=6378137 +b=6378137 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"


##Steps to creat each region map

## 1. Filter region of interest from all_rgn 
rgn_eez <- all_rgns_repr %>%
  dplyr::filter(rgn_id== 224) ## For loop rgn_id == i?

plot(rgn_eez[2])

## 2. Extract bounding box

rgn_bbox <- as.matrix(st_bbox(rgn_eez))
  

## 3. Create the base map with the corresponding bbox
rgn_loc <- rgn_bbox[1:4]
rgn_bmap <- get_map(location = rgn_bbox, zoom = 3, source = "google", maptype = "terrain", crop = FALSE)

plot(rgn_bmap)

## 4. Plot the eex and the base map. It is importatnt to do the CRS trasformation right before ploting both maps together in order to work.
st_crs(rgn_eez) <- 4326
rgn_tans <- st_transform(rgn_eez, crs = 3857)[1]
plot(st_geometry(rgn_tans), col = rgb(red = 1, green = 0, blue = 0, alpha = 0.2),border=NA, bgMap = rgn_bmap) #st_geometry removes the column name (rgn_id)
plot(st_geometry(rgn_tans), bgMap = rgn_bmap)




data <- fortify(shapefile)

qmap('chile', zoom = 3, maptype = 'satellite') +
geom_sf(data = rgn_eez,
colour = 'white', fill = 'black', alpha = .4, size = .3)

test <- qmap('chile', zoom = 3, maptype = 'satellite')+
  geom_sf(mapping = aes(), data= rgn_eez)


plot(test)



```










