---
title: "EEZ map for every OHI region"
author: "Camila Vargas"
date: "8/23/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document creates one global map for each region highlighting their EEZ and on "zoon-in" map per region indication their eez. This was done as part of the OHI global fellowship indepenetn project. 

## Setup

```{r}

library(doParallel)
library(rgdal)
library(raster)
library(sf)
library(tidyverse)
library(cowplot)
library(ggmap)
library(lwgeom)

source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2018/master/src/R/spatial_common.R')

#setwd("~/github/global-viz/region_maps")


```


### Region "zoom-in" map

The first step was to create a map highlinting each region eez. These maps where created using the med resolution shapefile find in [this folder](https://github.com/OHI-Science/ohiprep/tree/master/globalprep/spatial/downres). The shapefiles with the eez for each region ehate then combined with a base map using ggmap.


```{r}
## Read the shapefile for all regions and filter for eez (our area of interest for these maps)

all_rgns <- sf::st_read('../../ohiprep/globalprep/spatial/downres', layer="rgn_all_gcs_med_res") %>%
  dplyr::filter(rgn_typ == "eez") %>% 
  dplyr::select(rgn_id, rgn_key, geometry) %>% 
  dplyr::arrange(rgn_id)


##validate the map so it can be ploted

all_rgns <- st_make_valid(all_rgns)
plot(all_rgns[1])



## Forloop to creat a map for each region.




```




### Test with on region

TEsting the methods in one region (Chile), before running the loop (and building the loop in this case).

```{r}
##Steps to creat each region map

## 1. Filter region of interest from all_rgn 
rgn_eez <- all_rgns %>%
  dplyr::filter(rgn_id== 224) ## For loop rgn_id == i?

plot(rgn_eez)

## 2. Extract bounding box

rgn_bbox <- as.matrix(st_bbox(rgn_eez))
  

## 3. Create the base map with the corresponding bbox
rgn_loc <- rgn_bbox[1:4]
rgn_bmap <- get_map(location = rgn_loc, zoom = 3, source = "google", maptype = "terrain", crop = FALSE)

plot(rgn_bmap)

## 4. Plot the eex and the base map. It is importatnt to do the CRS trasformation right before ploting both maps together in order to work.
st_crs(rgn_eez) <- 4326
rgn_tans <- st_transform(rgn_eez, crs = 3857)[1]
png(filename ="figures/chile_eez.png", res=500, width=7, height=7, units="in", bg= "transparent")
plot_eez <- plot(st_geometry(rgn_tans), col = rgb(red = 1, green = 0, blue = 0, alpha = 0.2),border=NA, bgMap = rgn_bmap) #st_geometry removes the column name (rgn_id)
dev.off()

plot(plot_eez)

```


## Ceating inset maps for each region
The inset map is a worldmap where the eez of a specific region is highlighted. 

```{r}

## Wrangle region object imported from spatial_common.R
regions <- as(regions, "Spatial")
land <- regions[regions$rgn_type %in% c("land", "land-disputed", "land-noeez"), ]

# function to plot general regions
plot_rgn <- function(rgn){ #rgn="New Zealand"
  rgn_area <- regions[regions$rgn_name == rgn, ]  
  png(filename =str_to_lower(sprintf("figures/inset_maps/%s.png",str_replace(rgn, pattern = " ","_"))), res=500, width=7, height=7, units="in", bg= "transparent")
  plot(regions, col='#e3e7ea', border=NA)
  plot(land, col='gray85', border='grey80', add=TRUE, lwd=0.5)
  plot(rgn_area, col="#313695", border="#313695", add=TRUE)
  dev.off()
}

## Test the function for one region
plot_rgn("Chile")


##List with region names to loop over and create one inset map per region
region_list <- read_csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/spatial/regions_list.csv") 

##Loop through and save one map per region as a png
for (region in region_list$rgn_name) {#test with five regions[1:5]
 
  print(region)
  
  plot_rgn(rgn = region)  
}
```


## Combine both inset and zoom in region

Ideally, the inset map and the eez map would be combined in one figure in order to give a context of wherte the region is. Because of time constrains this is all the progress made here up to the complesion of this fellowship. 

Here some initial thought on how to go about this.

```{r}
## This package allows you to add images to a plot. 
library(magick)

##Create a plot with the eez map png
eez <- ggdraw()+
  draw_image("figures/chile_eez.png")

##Creat a plot with the inset png  
inset <- ggdraw()+
  #draw_image("figures/chile_eez.png", x = 0, y = 0, width = 1, height = 1, scale = 1)+
  draw_image("figures/inset_maps/chile.png",scale = 0.6, clip="on")

##Thought 1:
##Both images have the same hight and width. See where they where saves. So next step can by trying to remove the "transparent" space of the inset map and then try the draw image scale..

##This function plots one image next to the other
plot_grid(inset, eez)


## Thought 2: In order to make it easer to move the inset map around maybe it counf be possible to create a xy plot in ggplot and print the eez mp on top and the inset map at the corner.

ggplot(data.frame(x = 1:3, y = 1:3), aes(x, y)) +
    geom_point(size = 3) +
    draw_image("figures/chile_eez.png") +
    draw_image(img2, x = 2, y = 2, scale = .9)


## Example code to plot two images in one plot
img <- magick::image_read("http://jeroen.github.io/images/tiger.svg")
  img <- magick::image_transparent(img, color = "white")
  img2 <- magick::image_negate(img)
  ggplot(data.frame(x = 1:3, y = 1:3), aes(x, y)) +
    geom_point(size = 3) +
    geom_abline(slope = 1, intercept = 0, linetype = 2, color = "blue") +
    draw_image(img , x = 1, y = 1, scale = .9) +
    draw_image(img2, x = 2, y = 2, scale = .9)

  ggdraw()+draw_image(img)
  
##Thought 3: Seach on other packages, or option for ploting two images together.

```






