---
title: "Plot - region ranking and scores over time"
author: "Camila Vargas"
date: "9/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains the necesary code to plot scores of the OHI annual global sassesment over time for every region. And a ranking plot indicating the rank of every region in the specified assesment year. 
The plots are created using `ggplot2` and then converted to `plotly`. The ggplot version of these plots were created for the region summary cards and the plotly version for disply at http://ohi-science.org/ohi-global/scores

## Setup

```{r}
##Packages needed. If not install use: install.pakcage("")
library(tidyverse) #install.packages("tidyverse")
library(plotly) #install.packages("plotly")
library(readr) #install.packages()
library(cowplot) #install.packages("cowplot")
library(ggrepel) #install.packages("ggrepel")
library(RColorBrewer) #install.packages("RColorBrewer")
```


## Data

```{r}

## Location time series dataset with information for all regions' ids and names
score_data_loc <- "https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/scores.csv"

rgn_data_loc <- "https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/spatial/regions_list.csv"


## Read in the data
scores <- read.csv(score_data_loc) %>%
  rename(abb = "goal", rgn_id = "region_id")

region_names <- read.csv(rgn_data_loc, colClasses = c(rgn_name = "character")) %>% 
  select(rgn_id, rgn_name) 
```

## Wrangle data for time series plots

```{r}
## goals dataframe
goals <- c("Index", 
           "Artisanal Opporunities", 
           "Biodiversity",
           "Carbon Storage",
           "Clean Waters", 
           "Livelihoods and Economies",
           "Coastal Protection", 
           "Food Provision",
           "Natural Products", 
           "Sense of Place", 
           "Tourism and Recreation")

goals_abbrev <- c("Index", "AO", "BD", "CS", "CW", "LE", "CP", "FP", "NP", "SP", "TR")

goals_descrip <- c("Overall Ocean Health Index score", 
                   "Opportunity for small-scale fishers to supply <br> catch to their families, community or local market", 
                   "Conservation status of native marine species and key habitats", 
                   "Condition of coastal habitats that store and <br> sequester atmospheric carbon", 
                   "Degree to which oceans are free of contaminants such as  <br> chemicals, excessive nutrients, human pathogens, and trash", 
                   "Coastal and ocean-dependent livelihoods (job quantity and quality) <br> and economies (revenues) produced by marine sectors", 
                   "Amount of protection provided by marine and coastal habitats <br> serving as natural buffers against incoming waves", 
                   "Sustainable harvest of seafood from wild-caught <br> fisheries and mariculture ", 
                   "Natural resources that are sustainably extracted <br> from living marine resources", 
                   "Conservation status of iconic species and geographic <br> locations that contribute to cultural identity", 
                   "Value people have for experiencing and enjoying <br> coastal areas and attractions")

goals <-  data.frame(goal = goals, abb = goals_abbrev, description = goals_descrip)


##additional step to lable each line with the goal abbreviation
scores_description <- scores %>% 
  left_join(goals, by = "abb") %>% 
  mutate(label = ifelse(year == max(year), as.character(abb), NA_character_))


```


## Loop to create one plot for each region


```{r}

 for(rgn in region_names$rgn_id){ #rgn= region_names$rgn_id[224] - testing for one region
#for(rgn in c(70, 40, 224)) #testing for three regions
  
  ## subset score data for country/region
  rgn_score_data <- scores_description %>% 
    dplyr::filter(rgn_id == rgn) %>% 
    dplyr::filter(dimension == "score") %>% 
    dplyr::filter(abb %in% c("AO", "BD", "CP", "CS", "CW", "FP", "Index", "LE", "NP", "SP", "TR"))
  
  
  ## create time series plot
time_series_rgn_plot <- ggplot(rgn_score_data %>% filter(abb != "Index"),
                                 aes(x = year, y = score, color = goal)) +
    geom_line(data = rgn_score_data %>% filter( abb == "Index"),
              aes(x = year, y = score), size = 1.8, color = "gray20", alpha = 1) +
    geom_point(data = rgn_score_data %>% filter(abb == "Index"),
               aes(x = year, y = score, text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 2, color = "gray20") +
    geom_text_repel(data = rgn_score_data%>% filter( abb == "Index"),
        aes(label = label),
        na.rm = TRUE,
       fontface = "bold",
        hjust = 0,
        nudge_x = 0.1,
        nudge_y = 0,
        direction = "y",
        point.padding = unit(8, "points"),
        size = 3,
       segment.color = NA,
      color = "gray20")+
    geom_line(aes(group = goal), alpha = 1, size = 1) +
    geom_point(aes(text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 1.2) +
    scale_x_continuous(breaks = seq(2012, 2018, 1)) +
    labs(y = "Score", color = "Goal")+ 
    theme_cowplot() +
    theme(axis.title.x = element_blank(),
      legend.position = "bottom")+
    scale_color_brewer(palette = "Spectral") +
    guides(colour = guide_legend(override.aes = list(size = 3)))
  
  plot(time_series_rgn_plot)

  ##Save plots as pngs
  #
  
##Plotly for website. NOTE: ggrapel does not show up in the plotly

#ggplotly(chile_plot, tooltip="text") %>% 
 # config(displayModeBar = F)
  
}

```

## Wrangle data for rank plots


